\chapter{Simple Harmonic Motion}

Book chapter 17

\section{2020-09-15}

\subsection{Introduction}

\subsubsection{Every week}

\begin{itemize}
    \item Videos
    \item Meet Tuesday to discuss videos (synchronous part)
    \item Thursday is extended office hours
    \item Lab due Friday
    \item No midterms, but presentations
\end{itemize}

\subsubsection{Presentations}

\begin{itemize}
    \item Present in groups of 3 or 4, shuffled
\end{itemize}

\subsubsection{Environments to set up}

\begin{itemize}
    \item OpenGL Libraries
    \item Compute shaders not allowed on Mac?
    \item Windows - Use Visual Studio
    \item Linux - Ask Sydney
\end{itemize}

\subsection{Lecture}

\subsubsection{3D Graphics}

\begin{outline}
    \1 How to store 3D stuff?
        \2 Things are completely hollow
        \2 Surface is triangles. 3 points = a plane. 4 points = saddle
        \2 The 3D modeler has given you the mesh already
        \2 Easiest case: float triplets make a point, point triplets make a triangle
    \1 Rendering a triangle?
        \2 Screen has a fixed number of discrete pixels on a 2D screen
        \2 2 coordinate systems: world (3D float) and screen (2D int). 
        Matrix $\mathbf{M}$ such that $\mathbf{M}\vec{v_w} = \vec{v_s}$
        \2 Triangle needs to get filled in
    \1 Computation
        \2 First 3D graphics were done on single-core CPUs and were slow and primitive. 
        \2 Originally, CPU writes directly into VRAM that gets directly drawn to monitor, you see the image get drawn in front of you
        \2 Double-buffering: 2 VRAM buffers, write to A, copy A to B when finished, render B
        \2 Page-flipping: 2 VRAM buffers, write to A, render A and start writing to B, etc.
        \2 The VRAM alone is the original "graphics card"
        \2 Now, 150-250k triangles, offload them onto a highly parallel non-CPU processor (GPU), lots of tiny cores, bigger memory, store triangles and pictures on it
        \2 VRAM closer to GPU = higher clock rates
    \1 Shaders 
        \2 Copy data from RAM into VRAM
        \2 Write a shader to work on the memory (named so because it's often used for light calculations)
        \2 Scientists and engineers write shaders for matrices. The course is graphics and simulations

\end{outline}

\section{2020-09-16}