\chapter{Week 3}

\section{9/21 -- Hour 9}

\subsection{Writing Prompt}

\begin{outline}
    \1 5 Qualitative characteristics
        \2 Persistent, tenacious
        \2 Humble
        \2 Creative
        \2 Communicative
        \2 Curious
    \1 5 Action Verbs
        \2 Invent
        \2 Design
        \2 Research
        \2 Explore
        \2 Persevere
    \1 5 Career goals to accomplish
        \2 BSc. Computer Science
        \2 Minor in mathematics
        \2 Land 4th internship at FAANG
        \2 R\&D engineering
        \2 Find a mentor
    \1 5 personal, local, or worldly goals
        \2 Effect lasting, positive change for minority groups, using technology. \st{establish communism}
        \2 Discover cool new technologies
        \2 Enjoy the work I do and help ensure others can enjoy theirs
        \2 Never stop learning. Learn about many different fields.
        \2 Don't burn myself out. haha.
\end{outline}

\subsection{Branding}

Under Armour -- strong, militaristic, serious font

Apple -- clean, sleek, modern, lightweight, accessible

Chan's Chinese Restaurant -- ``Chinese Restaurant Font''

\subsubsection{Round 1}

Software engineer. Software scientist. Inventor. 

\subsubsection{Round 2}

\begin{itemize}
    \item Creating clever software solutions that don't keep you up at night with bugs
    \item Creating clever software solutions so you stay up at night with ideas, not worries
    \item Creating clean, clever solutions for your digital dreams.
    \item Building your ideas, one line of code at a time
    \item Creating clean solutions for your problems, one line of code at a time
    \item Solving your problems with well-designed apps, one line of code at a time
    \item Creating clean, clever solutions to build your ideas.
    \item Creating clever solutions that leave digital imprints on the world.
    \item Listener | Explorer | Debugger | Inventor
\end{itemize}

\subsection{Personal Bio}

\subsubsection{Round 1}

\begin{outline}
    \1 Internship at Micro-Vu
        \2 
    \1 Internship at FabTime
    \1 Student at Cal Poly
        \2 S
    \1 Internship at GoodRipple
\end{outline}

I am a software engineering intern whose goal is to empower users with software solutions. Ever since I taught myself Java back in 6th grade to build a Minecraft mod, I've been continuously going further, with more complex projects. I am now a computer science student at California Polytechnic State University, San Luis Obispo, where I am learning about cutting-edge graphics technology among other things. 

As a current software engineering intern at Micro-Vu, I work with the full-time engineers to build the upcoming InSpec 3 metrology software. In addition, I researched optimization algorithms for geometric tolerance fitting.

As a software engineering intern at FabTime, I improved their silicon wafer charting software to make it more user-friendly. Also, I seeked and eliminated difficult bugs in various languages, like VBScript, C, JavaScript, and SQL.

In my spare time, I like to work on software projects to sharpen my mind and skills, like my website, astrid.tech. When I'm not inventing new things, you can catch me cooking and sampling foods from various different cuisines. 

